\documentclass[english,a4paper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{natbib}
\usepackage{graphicx}  %%% for including graphics
\graphicspath{{./images/}}
\usepackage{url}       %%% for including URLs
\usepackage{times}
\usepackage[margin=25mm]{geometry}

%%% custom packages
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{hyperref}
\usepackage[autostyle=true]{csquotes}
\usepackage{xpatch}
%%% custom packages

\title{Lexical and Non-Lexical Analysis of Soldiers' Tweets\\- With Sentiment and Emotion Metrics}
\date{\today}

\author{
  Chao Chen, Chetan Prasad, Chen Wang, \\
  Rachit Rastogi, Sumit Mukhija \\
  School of Computer Science and Statistics, Trinity College Dublin\\
  \texttt{\{chenc1, cprasad, wangc5, rrastogi, mukhijas\}@tcd.ie}
}

\begin{document}
\maketitle
\thispagestyle{empty}
\pagestyle{empty}

\begin{abstract}
  A large number of war veterans are diagnosed with post traumatic stress disorder every day. This warrants a concern to evaluate the mental health of the war veterans. Existing works show that mental health changes caused by wars can be reflected in lexical and non-lexical features of the social media texts. In order to detect and compare those changes we collected data from 208 soldiers' tweets (n=6,61,342) with 280 civilians' tweets (n=6,00,173). We examined them with lexical and non-lexical aspects. Elements and attributes of tweets are processed and included as non-lexical features. Sentiment and emotion analysis is made on the corpora. We had a close look at the results with discussion and identified the differences between civilians and soldiers in both positive and negative directions. \\
  \textbf{Keywords:} Twitter, tweet, soldier, veteran, lexical, SentiWordNet, EmoLex, lexicon, sentiment, emotion
\end{abstract}

\input{introduction/introduction.tex}
\input{background/background.tex}
\input{experiment/experiment.tex}
\input{discussion/discussion.tex}
\input{conclusion/conclusion.tex}
\input{futurework/futurework.tex}

\clearpage

\bibliographystyle{chicago}
\bibliography{ref}

\end{document}
